Hierarchical Reverberation Mapping

### 2013-12-03 Paper/ms.tex
Paragraph describing sims

\section{Demonstration on Simulated Data}\label{sec:data}
To test our hierarchical model, and compare it to the stacked cross-correlation
function, we simulated data from 100 AGN. The data for each object was
continuum flux measurements, once per day, for 100 days. The continuum fluxes
for each object oscillate around a mean value of 50 in arbitrary units, and the
standard deviation of the measurement noise is 1 (i.e. 2\%). The line data is measured on
only two days, with times selected from a uniform distribution between $t=50$
and $t=100$ days (i.e. corresponding to the latter half of the continuum data).
The flux of the line data is scaled to half that of the line data, and the
measurement noise for the line data is 0.25, or 1\%. See Figure~\ref{fig:data}
for three illustrative data sets from the sample.

>>>>

\section{Demonstration on Simulated Data}\label{sec:data}
To test our hierarchical model, and compare it to the stacked cross-correlation
function, we simulated data from a sample of 100 AGN. We assumed the
continuum flux for each object fluctuates around a mean value $m = 50$ in
arbitrary units. The variability timescales $L$ were simulated from a very
broad log-uniform distribution (i.e. a uniform distribution for $\ln(L)$)
with a lower limit of 100 days and an upper limit of $10,000$ days. The
variability amplitudes $\beta$ were also simulated from a log-uniform
distribution with lower limit of 0.2 flux units and an upper limit of 1 flux
unit. This implies some objects are more variable than others, as is typical
in reverberation mapping.

The measured data for each of the 100 AGN was
continuum flux measurements, once per day, for 100 days. The continuum fluxes
for each object oscillate around a mean value of 50 in arbitrary units, and the
standard deviation of the measurement noise is 1 (i.e. 2\%). The line data is measured on
only two days, with times selected from a uniform distribution between $t=50$
and $t=100$ days (i.e. corresponding to the latter half of the continuum data).
The flux of the line data is scaled to half that of the line data, and the
measurement noise for the line data is 0.25, or 1\%. See Figure~\ref{fig:data}
for three illustrative data sets from the sample.
